Call Center Regression Data Analysis

### 2022-11-30 References/Manuscript.tex
commit #cleanup simulation

The Projected Calls Per Day simply came from the total calls per week * the RatioDayPerWeek. We can also see this approach worked relatively well in the forecasting model. 

@@

  From there I ran Correlation between CallsPerAgent and the dependent variables. The Pearson Product Moment Correlation test can take a range of values from 1 to -1. A value of 0 shows there is no association between two variables. 
A value greater than 0 indicates a positive association, meaning as the value of the dependent variable increases so does the independent variable. A value less than 0 indicates a negative association, meaning as the dependent 
variable decreases so does the independent variable. The stronger the correlation between the variables the higher it is to 1 or -1.  The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value. 
The one dependent variable is CallsPerAgent. In this case, the Calltime is the same as Handletime, which is the combination of Wait time, Hold time, and Wrap Up Time. 
The Average Goal Being Met would be whatever the business establishes in seconds of  how long they would want a call center call to last. Average Interaction Value would be at what percentage 
they want calls being "Handled" or taken by an agent in anyway. 
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l |}
    {\bf Dependent Variable} & {\bf Correlation Coefficient}\\
  \hline
  Wait Time& 0.405 \\
  \hline
  Call Time& 0.238\\
  \hline
  Goal Met& -0.496  \\
  \hline
  Interaction Value& 0.484\\
  \end{tabular}
  }
  \end{table}
Typically, a Pearson's coefficient ranging between plus or minus .3 represents a small association, while a Pearson's coefficient
ranging between plus or minus .3 to .5 represents a medium association, and anything over plus or minus .5 represents a large association.
Wait Time and Calls Per Agent have a medium positive relationship which states as Calls Per Agent increases, so does the Wait Time for 
each Caller. Call Time and Calls Per Agent have a small positive relationship which states as Calls Per Agent increases, so does the 
Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is nothing being hit consistently when Calls 
are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should
be more abandoned calls, but according to Pearsons Coefficient this is not the case. So while this relationship may not be a linear one,
I will still present a model for it.

>>>>

The Projected Calls Per Day simply came from the Total calls per week * the RatioDayPerWeek. We can also see this approach worked relatively well in the forecasting model. 

@@

  From there I ran Correlations between CallsPerAgent and the dependent variables. The Pearson Product Moment Correlation test can take a range of values from 1 to -1. A value of 0 shows there is no association between two variables. 
A value greater than 0 indicates a positive association, meaning as the value of the dependent variable increases so does the independent variable. A value less than 0 indicates a negative association, meaning as the dependent 
variable decreases so does the independent variable. The stronger the correlation between the variables the closer it is to 1 or -1.  The 4 dependent variables were Average Wait Time, Average Call Time, Average Goal Being Met, Average Interaction Value. 
The one dependent variable is CallsPerAgent. In this case, the Calltime is the same as Handletime, which is the combination of Wait time, Hold time, and Wrap Up Time. 
The Average Goal Being Met would be whatever the business establishes in seconds of  how long they would want a call center call to last. Average Interaction Value would be at what percentage 
they want calls being "Handled" or taken by an agent in anyway. 
\begin{table}[H]
  \resizebox{\textwidth}{!} {
  \begin{tabular}{ l | l |}
    {\bf Dependent Variable} & {\bf Correlation Coefficient}\\
  \hline
  Wait Time& 0.405 \\
  \hline
  Call Time& 0.238\\
  \hline
  Goal Met& -0.496  \\
  \hline
  Interaction Value& 0.484\\
  \end{tabular}
  }
  \end{table}
Typically, a Pearson's coefficient ranging between plus or minus .3 represents a small association, while a Pearson's coefficient
ranging between plus or minus .3 to .5 represents a medium association, and anything over plus or minus .5 represents a large association.
Wait Time and Calls Per Agent have a medium positive relationship which states as Calls Per Agent increases, so does the Wait Time for 
each Caller. Call Time and Calls Per Agent have a small positive relationship which states as Calls Per Agent increases, so does the 
Call Time. Goal Time and Calls Per Agents have the strongest relationship, in this case a negative medium relationship, which states as
Calls Per Agents increases, the Goal Being Met decreases. This means the Average Goal Time is not being hit consistently when Calls 
are increasing. Interaction Value and Calls Per Agent have a medium positive relationship. However, in theory, as calls increase there should
be more abandoned calls, but according to Pearsons Coefficient this is not the case. So while this relationship may not be a linear one,
I will still present a model for it.
